Homework 1

### 2019-09-05 MSimonsHW1.tex
HW1 Prob 3

\item \textbf{} If $3 \nmid n$, then, by the Division Algorithm, either $n = 3k + 1$ or $n = 3k + 2$ for some integer $k$.  First, assume $n = 3k + 1$.  Thus, $n^1 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.  Therefore, $3 \vert (n - 1)^2$ for this case.  Next, assume $n = 3k + 2$.  Thus, $n^1 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.  Therefore, $3 \vert (n - 1)^2$ for all $n$ such that $3 \nmid n$.

\item \textbf{} TODO

>>>>

\item If $3 \nmid n$, then, by the Division Algorithm, either $n = 3k + 1$ or $n = 3k + 2$ for some integer $k$.  First, assume $n = 3k + 1$.  Thus, $n^1 - 1 = (3k + 1)^2 - 1 = 3 * (3k^2 + 2k)$.  Therefore, $3 \vert (n - 1)^2$ for this case.  Next, assume $n = 3k + 2$.  Thus, $n^1 - 1 = (3k + 2)^2 - 1 = 3 * (3k^2 + 4k + 1)$.  Therefore, $3 \vert (n - 1)^2$ for all $n$ such that $3 \nmid n$.

\item Let $a = {p_1}^{x_1} * ... * {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ... * {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.  Let $c = {q_1}^{z_1} * ... * {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.  This holds because $(a, c) = 1$ and $(b, c) = 1$, meaning $a$ and $c$ have no common prime factors and $b$ and $c$ have no common prime factors.  Thus, $ab = {p_1}^{x_1 + y_1} * ... * {p_k}^{x_k + y_k}$.  Therefore, $ab$ and $c$ also do not have any common prime factors.  This imples that $(ab, c) = 1$.

\item TODO 4

\item TODO 5

\item TODO 6

\item TODO 7
